Twisted 11-dimensional supergravity, I

### 2021-08-05 draft.tex
descendant

If $d \ne 3$ then there is the following subcomplex $\til{\cE}_{KS}\subset \cE_{\rm KS}$ defined by:
\[
\begin{tikzcd}
\ul{-1} & \ul{0} & \cdots & \ul{d-4} & \ul{d-3} & \cdots    \\
\PV^{1,\bu} \ar[r] & u\PV^{0,\bu} & & & & &  \\
& & & \PV^{d-2, \bu} \ar[r] & u \PV^{d-3, \bu} \ar[r] & \cdots &   .
\end{tikzcd}
\]
And one can check that the shifted Poisson bivector restricts to a shifted Poisson bivector on this subcomplex. 
Thus, we have the following.

@@

\begin{lem}
The restricted action $I_{pot} = \Phi^* I_{BCOV}$ has $\CC^\times$ weight $+1$. 
In particular, the non-linear BRST operator 
\[
\delta_{pot} = Q_{pot} + \{I_{pot},-\}
\]
is $\CC^\times$ weight zero.
\end{lem}

>>>>

If $d \ne 3$ then there is the following subcomplex $\til{\cE}_{KS}\subset \cE_{\rm KS}$ defined by:
\beqn\label{eqn:tilks}
\begin{tikzcd}
\ul{-1} & \ul{0} & \cdots & \ul{d-4} & \ul{d-3} & \cdots    \\
\PV^{1,\bu} \ar[r] & u\PV^{0,\bu} & & & & &  \\
& & & \PV^{d-2, \bu} \ar[r] & u \PV^{d-3, \bu} \ar[r] & \cdots &   .
\end{tikzcd}
\eeqn
And one can check that the shifted Poisson bivector restricts to a shifted Poisson bivector on this subcomplex. 
Thus, we have the following.

@@

There is also a $\CC^\times$ action on the fields $\til{\cE}_{KS}$ of Kodaira--Spencer theory by declaring the first line in \eqref{eqn:tilks} is weight zero and the second line is weight $+1$.

\begin{lem}
The restricted action $I_{pot} = \Phi^* \til{I}_{BCOV}$ has $\CC^\times$ weight $+1$. 
In particular, the non-linear BRST operator 
\[
\delta_{pot} = Q_{pot} + \{I_{pot},-\}
\]
is $\CC^\times$ weight zero.
\end{lem}
\begin{proof}
The map $\Phi \colon \cE_{pot} \to \til{\cE}_{KS}$ preserves $\CC^\times$ weight, so it suffices to prove that $I_{BCOV}$ is weight $+1$. 
We will make use of two gradings on $\til{\cE}_{KS}$. 
The first is by holomorphic polyvector field type, and the second is by descendant degree.
The summand $u^l \PV^{k,\bu}$ is polyvector type $k$ and descendant degree $l$.

We introduce notation in this proof that won't be used later on. 
Let $\alpha$ denote a super field living in the first line of \eqref{eqn:tilks} and let $\beta$ denote a super field living in the second line of \eqref{eqn:tilks}.
If a field of type $\alpha$ has polyvector type $k$ then it has descendant degree $1-k$, $k=0,1$. 
If a field of type $\beta$ has polyvector type $l$ then it has descendant degree $d-2-l$.

A homogenous polynomial degree term in the BCOV action $I_{BCOV}$ is linear combination of functionals of the form
\[
\int_\Omega \alpha_1 \wedge \cdots \wedge \alpha_m \wedge \beta_1 \wedge \cdots \wedge \beta_n  .
\]
Let $k_i$ be the polyvector field type of $\alpha_i$ and let $l_j$ be the polyvector field type of $\beta_j$. 
In order for this expression to contribute nontrivially to the BCOV action two constraints must hold:
\begin{align*}
\sum_{i=1}^m k_i + \sum_{j=1}^n l_j & = d \\
\sum_{i=1}^m (1-k_i) + \sum_{j=1}^n (d-2-l_j) & = m+n-3 .
\end{align*}
The first constraint ensures that the integrand is of top polyvector degree. 
The second constraint is on the descendant degree, see \brian{ref above}.

Simplifying these two equations, one finds the condition
\[
m+n-3 = m+(d-2)n - d 
\]
which implies $n=1$, as desired. 
\end{proof}
